Enhancement of SDR in Thessaloniki Clear Sky

### 2024-05-09 GHI_enh_CSid.tex
Commit 2024-05-09 19:12

\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_mean}

\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \FloatTok{0.86}

\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ trend\_factor)]}

@@

@@

\NormalTok{  test }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}
    \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{*}\NormalTok{ x)),}
    \FunctionTok{mean}\NormalTok{(wattGLB)),}
\NormalTok{       by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}

@@

\FunctionTok{optimise}\NormalTok{(f, }\AttributeTok{interval =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{1.8}\NormalTok{), }\AttributeTok{maximum =}\NormalTok{ F, }\AttributeTok{tol =} \FloatTok{0.0001}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$minimum
[1] 0.2000654

$objective
[1] 8619.603
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(DTdaily[, En\_Ref\_sum, Day])}
\FunctionTok{plot}\NormalTok{(DTdaily[, glo\_Sum, Day])}
\FunctionTok{plot}\NormalTok{(DTdaily[, GLB\_Sum, Day])}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-20} \end{center}

\begin{verbatim}
$minimum
[1] 0.8593852

$objective
[1] 0.6165028
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-21} \end{center}

\begin{verbatim}
[1] 0.6615997
\end{verbatim}

@@

\begin{verbatim}
$mae
[1] 97.0816

$mse
[1] 9657.575

$rmse
[1] 98.27296

$mape
[1] 0.1672027

$nmse
[1] 45.49449

$rstd
[1] 0.1688189
\end{verbatim}

>>>>

\DocumentationTok{\#\# for trend mean}
\CommentTok{\# trend\_apply  \textless{}{-} trend\_mean}
\CommentTok{\# trend\_factor \textless{}{-} {-}0.01995656}
\DocumentationTok{\#\# for trend median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}

\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{+}\NormalTok{ trend\_factor)]}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{rmserr}\NormalTok{(DATA}\SpecialCharTok{$}\NormalTok{Thresh\_test, DATA}\SpecialCharTok{$}\NormalTok{wattGLB)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$mae
[1] 85.55033

$mse
[1] 8567.15

$rmse
[1] 92.5589

$mape
[1] 0.1365803

$nmse
[1] 0.1436112

$rstd
[1] 0.1400624
\end{verbatim}

@@

\NormalTok{  test }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}
    \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{+}\NormalTok{ x)),}
    \FunctionTok{mean}\NormalTok{(wattGLB)),}
\NormalTok{       by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}

@@

\FunctionTok{optimise}\NormalTok{(f, }\AttributeTok{interval =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{0.02}\NormalTok{, }\FloatTok{0.02}\NormalTok{), }\AttributeTok{maximum =}\NormalTok{ F, }\AttributeTok{tol =} \FloatTok{0.0001}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$minimum
[1] -0.01995656

$objective
[1] 7042.576
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(DTdaily[, En\_Ref\_sum, Day])}
\FunctionTok{plot}\NormalTok{(DTdaily[, glo\_Sum, Day])}
\FunctionTok{plot}\NormalTok{(DTdaily[, GLB\_Sum, Day])}
\FunctionTok{plot}\NormalTok{(DTdaily[, Thresh\_sum, Day])}

@@

@@

\begin{verbatim}
$mae
[1] 83.65625

$mse
[1] 7337.38

$rmse
[1] 85.65851

$mape
[1] 0.1442124

$nmse
[1] 34.56461

$rstd
[1] 0.1471491
\end{verbatim}
